---
title: 'OncoSimulR: Simulating pathways and mutual exclusivity.'
author: "Blanca Lacruz Pleguezuelos, Víctor Mateos Cáceres, Manuel Moradiellos Corpus"
date: "`r Sys.Date()`"
output:
  bookdown::html_document2:
    css: custom4.css
    toc: yes
    toc_float: yes
    fig_retina: null
classoption: a4paper
geometry: margin=3cm
fontsize: 12pt
bibliography: trabajo_oncosimul.bib
biblio-style: "apalike"
link-citations: true
vignette: >
  %\VignetteIndexEntry{OncoSimulR: Simulating pathways and mutual exclusivity.}
  %\VignetteEngine{knitr::rmarkdown} 
  %\VignettePackage{OncoSimulR} 
  %\VignetteEncoding{UTF-8} 
  %\VignetteDepends{OncoSimulR}
---

```{r setup, include = FALSE}
time0 <- Sys.time()
knitr::opts_chunk$set(echo = TRUE, collapse = FALSE)
options(width = 70)
require(BiocStyle)
require(pander)
library(OncoSimulR)
```

Vignettes are long form documentation commonly included in packages. Because they are part of the distribution of the package, they need to be as compact as possible. The `html_vignette` output type provides a custom style sheet (and tweaks some options) to ensure that the resulting html is as small as possible. The `html_vignette` format:

- Never uses retina figures
- Has a smaller default figure size
- Uses a custom CSS stylesheet instead of the default Twitter Bootstrap style

## Vignette Info

Note the various macros within the `vignette` section of the metadata block above. These are required in order to instruct R how to build the vignette. Note that you should change the `title` field and the `\VignetteIndexEntry` to match the title of your vignette.

## Styles

The `html_vignette` template includes a basic CSS theme. To override this theme you can specify your own CSS in the document metadata as follows:

    output: 
      rmarkdown::html_vignette:
        css: mystyles.css

## Figures




You can enable figure captions by `fig_caption: yes` in YAML:

    output:
      rmarkdown::html_vignette:
        fig_caption: yes

Then you can use the chunk option `fig.cap = "Your figure caption."` in **knitr**.

## More Examples

You can write math expressions, e.g. $Y = X\beta + \epsilon$, footnotes^[A footnote here.], and tables, e.g. using `knitr::kable()`.

```{r, echo=FALSE, results='asis'}
knitr::kable(head(mtcars, 10))
```

Mi super vieja:
```{r example5_fitness, message=FALSE}
fitness_rel <- function(a, b, r, g, gt = c("WT", "S", "I", "D")) {
    data.frame(
      Genotype = gt,
      Fitness = c("1",
                  paste0("1 + ", a, " * f_D"),
                  paste0("1 + 1 - ", g),
                  paste0("1 + (1 - f_I - f_D) * (1 - ", b, " + ", 
                         a, ") + f_I * (1 - ", b, " + ", r,
                         ") + f_D * (1 - 2 * ", b, ") + 1 - ", b, 
                         " + ", a, " + f_I * (", r, " - ",
                         a, ") - f_D * (", b, " + ", a, ")"))
                  )
}
```

```{r example5scen1, message=FALSE}
scen1 <- allFitnessEffects(genotFitness = fitness_rel(a = 0.5, b = 0.7,
                                                     r = 0.1, g = 0.8),
                          frequencyDependentFitness = TRUE,
                          frequencyType = "rel")

set.seed(1)
simulScen1 <- oncoSimulIndiv(scen1,
                              model = "McFL",
                              onlyCancer = FALSE,
                              finalTime = 70,
                              mu = 1e-4,
                              initSize = 5000,
                              keepPhylog = TRUE,
                              seed = NULL,
                              errorHitMaxTries = FALSE,
                              errorHitWallTime = FALSE)
op <- par(mfrow = c(1, 2))
plot(simulScen1, show = "genotypes", type = "line",
     main = "First scenario",
     cex.main = 1.4, cex.lab = 1.1,
     las = 1)
plot(simulScen1, show = "genotypes",
     main = "First scenario",
     cex.main = 1.4, cex.lab = 1.1,
     las = 1)
par(op)
par(mfrow = c(1, 1))
plot(simulScen1, show = "genotypes",
     main = "First scenario",
     cex.main = 1.4, cex.lab = 1.1,
     las = 1)
```

@uriarte17

Also a quote using `>`:

> "He who gives up [code] safety for [code] speed deserves neither."
([via](https://twitter.com/hadleywickham/status/504368538874703872))
